{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Some Bullet Points for Outlook Section

@@

>>>>

	\paragraph{Insights from Simulation cannot be Extended to More General Functions}

	\paragraph{Collinearity Problems in Basis Expansion Regression}

	\paragraph{Low Number of Basis Functions in FPCR Regression}

@@

	\paragraph{Orthogonal Polynomials to Solve Collinearity Problems of Monomial Basis}

	\paragraph{Comparison to Penalty Based Smoothing Procedures}
